On the probability of finding nonphysical solutions through shadowing\tnoteref{1}

### 2021-04-23 letter/responseToReviewers.tex

1. \reviewerOne{There are some published articles that support some conclusions of this manuscript...All of these should give the authors more information about the topic related to this manuscript}

We thank the reviewer for pointing out multiple references that support the conclusions of the present paper. In our revised manuscript, we have added them to our discussion section 5 (the edits are highlighted in \reviewerOne{red}), where we had originally referred to Clean Numerical Simulation (CNS).

2. \reviewerOne{There is another thing that might be mentioned.  Periodic solutions of some chaotic systems, such as three-body system, have physical meanings.  Although three-body systems are chaotic in essence, periodic orbits of three-body system indeed exist.}

Thank you for pointing this important point out. In our paper, we use ``nonphysicality'' to mean ``atypicality'' in the following sense, which, as you point out, may not be physically meaningless. Whenever an initial condition is sampled from a set of full Lebesgue measure in an open set, known as the attractor basin, that contains the chaotic attractor, the ergodic average along the orbit starting from that initial condition is equal to the ensemble average. This latter ensemble average or phase-space average is with respect to an SRB-type probability measure, which is called a {\em physical} measure (Ref. 10) since it is ``observed'' through ergodic averages along almost every orbit starting in the attractor basin. Thus, we refer to as ``nonphysical'' atypical orbits that do not produce the correct statistics associated with the SRB measure.

Nevertheless, the collection of unstable periodic orbits is intimately connected with the statistical properties of the strange attractor. Ensemble averages can be realized as weighted ergodic averages along long unstable periodic orbits (e.g. see Property 3.10 of \cite{llave}). Dynamical determinants, which are calculated on the set of periodic orbits, are connected with spectral resonances or the slowest correlation decay rates \cite{baladi-book}. Apart from these theoretical connections, the set of unstable periodic orbits is also recognized as a physically interpretable ``skeleton'' of an attractor \cite{cvitanovic1}. Besides providing alternative methods to calculate dynamical properties, the tangencies on unstable periodic orbits are thought to play an important role in attractor crises: a large statistical response to small system parameter perturbations \cite{berry}\cite{grebogi1}.

In section 3.2, we have expanded on these ideas without going into mathematical details of unstable periodic orbits, which would be beyond the scope of this paper. Thank you very much once again for this suggestion!

### 2021-04-23 main_els.tex
Add all of Liao's refs.

In view of the plucked tent map, we can further question the
validity of numerical solutions. Can numerical solutions play 
the role of the plucking perturbation to the 
governing equation? That is, can numerical solutions represent 
slight perturbations to the governing equations for which the physical 
distribution is drastically different from the physical distribution 
of the original governing equation? Sauer \cite{sauer} has shown 
examples in which numerical error due to computation in double-precision floating point arithmetic causes significant change in the stationary probability distribution on the attractor; other works \cite{cns} further analyze the unreliability due to double-precision arithmetic of statistical measures such as power spectra and correlation functions. The plucked tent map adds to this list of examples by demonstrating a mechanism to produce an extreme non-smooth response (Supplementary Material section \ref{sec:pluckedTentMap}). Uniformly hyperbolic 
dynamical systems exhibit \emph{linear response} 
(\cite{ruelle}\cite{baladi}) by which small parameter perturbations 
lead to small changes in statistics, which can be expanded as Taylor series around the reference parameter value. But, uniform hyperbolicity is a mathematical idealization, and although some physical systems have been observed to behave as if they were uniformly hyperbolic \cite{gallavotti}, a violation of uniform hyperbolicity is also prevalent in physical systems
\cite{wormell}\cite{lucarini}.

>>>>

In view of the plucked tent map, we can further question the
validity of numerical solutions. Can numerical solutions play 
the role of the plucking perturbation to the 
governing equation? That is, can numerical solutions represent 
slight perturbations to the governing equations for which the physical 
distribution is drastically different from the physical distribution 
of the original governing equation? Sauer \cite{sauer} has shown 
examples in which numerical error due to computation in double-precision floating point arithmetic causes significant change in the stationary probability distribution on the attractor. \reviewerOne{Some authors \cite{cns2}\cite{cns3} resort to Clean Numerical Simulations to tackle scenarios that demand highly accurate long-term prediction of chaotic orbits. When using double-precision arithmetic however, these works  \cite{cns}\cite{cns1}\cite{cns2}\cite{cns3} show that large errors result in statistical measures such as power spectra and spatio-temporal correlation functions.} The plucked tent map adds to this list of examples by demonstrating a mechanism to produce an extreme non-smooth response (Supplementary Material section \ref{sec:pluckedTentMap}).

Uniformly hyperbolic 
dynamical systems exhibit \emph{linear response} 
(\cite{ruelle}\cite{baladi}) by which small parameter perturbations 
lead to small changes in statistics, which can be expanded as Taylor series around the reference parameter value. But, uniform hyperbolicity is a mathematical idealization, and although some physical systems have been observed to behave as if they were uniformly hyperbolic \cite{gallavotti}, a violation of uniform hyperbolicity is also prevalent in physical systems
\cite{wormell}\cite{lucarini}.
